\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
methods

We want to test our model on a motion detection task on a binary stream of events. This type of signal, typically recorded by a Dynamic Vision Sensor (DVS), is a good representation of the information sent by the retinal ganglion cells through the optic nerve. With binary events, the visual system is able to capture the dynamics of a natural scene and perform various cognitive tasks in a fast and efficient fashion. To train and test our model, we need to define a dataset for which we control for motion direction and velocity. 
First, let's define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. A specific mechanism to do so are called saccades which are rapid eye movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average $2$ each second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of % N-V-phi

@@

\subsubsection{The general model}

>>>>

We want to test our model on a motion detection task on a realistic stream of events. This type of signal, typically recorded by a Dynamic Vision Sensor (DVS), is a good representation of the information and inspired by that sent by the retinal ganglion cells through the optic nerve. With binary events, the visual system is able to capture the dynamics of a natural scene and perform various cognitive tasks in a fast and efficient fashion. To train and test our model, we need to define a dataset for which we control for motion direction and velocity.  First, let's define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. A specific mechanism to do so are called saccades which are rapid eye movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average $2$ each second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of % N-V-phi

@@

\subsubsection{The heterogeneous synaptic delay model}
